### 2017-08-15 background.tex
added ref to foster paper and fixed various minor typos

Formal privacy techniques, such as homomorphic encryption, secure multiparty computation, and
other cryptographic solutions for protecting private data, often require significant computational
overhead \cite{gentry2012fully,naehrig2011can}. Prior work on database solutions
\cite{popa2011cryptdb} demonstrate the need for matching the privacy protecting techniques to the type of
numerical analyses in question to reduce overheads. 
Recent approaches for applying privacy techniques to
securely compute mathematical operations at large scale incur a 2x overhead~\cite{kepner2014computing}.
Nevertheless, the majority of the work in this area is focused on the security of numerical data, while the datasets
we focus on are mostly large volumes of unstructured and textual data.

@@

\NAME currently manages over 10TB of compressed text data and in the past year
alone, its analyses have consumed over 0.25M core hours by a single team. With a cloud-hosted system
such as \NAMENS, designed to enable large scale computational analyses over large datasets,
the overheads of formal privacy techniques are financially impractical. More importantly,
these techniques often do not lend themselves to secure analysis of arbitrary text data. 
The system thus protects the hosted micro-data by leveraging the strong security
guarantees of the cloud vendor's infrastructure and by utilizing strong access control
models. Some of the sensitive datasets managed in \NAME include JSTOR, Web of Science, IEEE,
and the UChicago grants database. Each has varying sensitivities and legal requirements associated with the
protection of microdata.

>>>>

Formal privacy techniques, such as homomorphic encryption, secure multiparty computation, and
other cryptographic solutions for protecting private data, often require significant computational
overhead \cite{gentry2012fully,naehrig2011can}. Prior work on database solutions
\cite{popa2011cryptdb} demonstrates the need to match privacy protecting techniques to the type of
numerical analyses in question to reduce overheads.
Kepner et al.~\cite{kepner2014computing} apply specialized techniques to perform
linear algebra operations at large scale with only a factor of two overhead.
Nevertheless, the majority of the work in this area is focused on the security of numerical data, while the datasets on which we are focused here 
are mostly large volumes of unstructured and textual data.

@@

\NAME currently manages over 10TB of compressed text data and in the past year
alone, its analyses have consumed over 0.25M core hours by a single team. With a cloud-hosted system
such as \NAMENS, designed to enable large scale computational analyses over large datasets,
the overheads of formal privacy techniques are financially impractical. More importantly,
these techniques often do not lend themselves to secure analysis of arbitrary text data. 
The system thus protects the hosted micro-data by leveraging the strong security
guarantees of the cloud vendor's infrastructure and by utilizing strong access control
models. Some of the sensitive datasets managed in \NAME include JSTOR, Web of Science, IEEE,
and the UChicago grants database. Each has varying sensitivities and legal requirements associated with the
protection of data about individuals: so called \emph{microdata}.

### 2017-08-15 introduction.tex
added ref to foster paper and fixed various minor typos

While science has long been collaborative and data driven, today, more than ever before,
researchers are dependent on technologies that enable their ability to safely store,
effectively manage, and quickly analyze vast amounts of
data. Moreover, individual datasets that are of interest to science and scholarship
vary widely in size, often take on heterogeneous structures, and command varying
levels of sensitivity. In fact, data sensitivity is often `custom' -defined specifically by
data use agreements that can be so granular as to vary from user to user and institution
to institution. At the very same time, however, a typical research setting involves
collaborators from multiple institutions that often share data, analysis techniques,
and results. This is, in fact, a cornerstone of modern research. Yet, when data are
particularly sensitive and their usage agreements limit access and research activities at the
level of individual users, research collaboration can either lead to inadvertent
breaches of agreement or can grind to a halt under administrative friction.

@@

At the same time, data sensitivity and security concerns are well founded. While many datasets are public, the most
valuable ones are often considered `private' or `protected' due to legal or contractual obligations under which the data
is shared, or even, the most extreme cases, under governmental regulation. However, the limited and proprietary nature
of particular datasets can further increase perceived value to researchers given that the space of possible
questions and possible answers that can be derived from the data is, in a sense, hidden from competition.
Simultaneously, increasing sensitivity adds to the burden of ensuring the security of the data.

>>>>

While science has long been collaborative and data driven, today, more than ever before,
researchers are dependent on technologies that enable their ability to safely store,
effectively manage, and quickly analyze vast amounts of
data. Moreover, individual datasets that are of interest to science and scholarship
vary widely in size, often take on heterogeneous structures, and command varying
levels of sensitivity. In fact, data sensitivity is often `custom'---defined specifically by
data use agreements that can be so granular as to vary from user to user and institution
to institution. At the same time, however, a typical research setting involves
collaborators from multiple institutions that often share data, analysis techniques,
and results. This is, in fact, a cornerstone of modern research. Yet, when data are
particularly sensitive and their usage agreements limit access and research activities at the
level of individual users, research collaboration can either lead to inadvertent
breaches of agreement or can grind to a halt under administrative friction.

@@

At the same time, data sensitivity and security concerns are well founded. While many datasets are public, the most
valuable ones are often considered `private' or `protected' due to legal or contractual obligations under which the data
is shared, or even, the most extreme cases, under governmental regulation. However, the limited and proprietary nature
of particular datasets can further increase perceived value to researchers given that the space of possible
questions and possible answers that can be derived from the data is, in a sense, hidden from competition.
Simultaneously, increasing sensitivity adds to the burden of ensuring data security.
